---
title: "Lab 00 - Hello IDS!"
author: "GANDOM MOGHADDAM"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Ben", "Dylan", "Adam", 
           "Jamie", "Gigi" , "Yara"),
  github_username = c("Gand0m", "ben-251", "adcel27", 
                      "jamieewen", "yarakanaann", "dylanhobman"), 
  colour = c("powderblue", "plum", "green", 
             "red", "peachpuff", "lightgreen"),
  hobby = c("Trampolining","badminton","skiing",
            "Football","Volleyball", "basketball"),
  favourite_number = c(2, 6, 3, 9, 4,7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The team members favorite numbers in a bar chart coloured in our favorite colours labeled by our usernames

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "usernames", 
          y = "favorite number (between 1-10",
          title = "Table 4 team members")
```

changing axis, legend, and plot labels

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

If the y axis value was our usernames
